### 2021-06-09 paper/report.tex
Formatting, mostly.

@@

Modelling a population of agents according to actual demographic characteristics means
that we can use a wide array of data to identify and estimate the model's many
parameters.\footnote{See section S.XXX of the supplementary materials for an
    overview.} Mobility data is used to
model the reductions in work contacts. School and daycare policies are incorporated
directly from official directives. Infection rates by age and geographical region are
estimated to match to officially recorded numbers; so is the prevalence of virus
strains. The model yields total infections, but only a fraction of those will be
officially recorded. We model the fraction of known cases as depicted in
Figure~\ref{fig:model_for_official_cases}.\comment[id=HM]{Add a sentence.}
\footnote{EQUATIONS FOR THE FOURTH PICTURE (find names!):

    The probabilities for Figure~\subref{fig:model_for_official_cases} are the
    following:

    \begin{align*}
        x & = \frac{n\_newly\_infected \times share\_known\_cases \times P(PCR | S)}{n\_symptomatic\_and\_untested}                    \\
        y & = \frac{n\_newly\_infected \times share\_known\_cases \times P(PCR | S)}{n\_asymptoptomatic\_and\_infected\_and\_untested} \\
        z & = \frac{P(PCR | RT)}{survey}
    \end{align*}
    where untested means that individuals are not waiting on the result of a previously
    administered rapid test.} A further advantage is that the simulated data have a
structure that resembles datasets used for regression models, which allows
additional plausibility checks by re-running the same models on the model-generated
data.\comment[id=HM]{Only keep if we actually do something like that.}

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/full_decomposition}

@@

The largest effect---almost one half when considering the decompositions---comes from
rapid testing. Here, it is crucial to differentiate between recorded cases and actual
cases. Additional testing means that infections become known which would otherwise
remain undetected. Figure~\ref{fig:2021_scenarios_recorded} shows that this means that
until late April, recorded cases are higher than in the scenario where none of the three
mechanisms is turned on. Compared to the scenario with vaccinations only, this point is
reached only around mid May and it would be June for the comparison with the
seasonality-only scenario. The effect on total cases, however, kicks in immediately and
strongly. Despite the fact that only a small fraction of the population performed weekly
rapid tests in March (X\%\comment[id=HM]{Put in}), the rise in new infections would be
limited by XXX\% relative to the scenario without vaccinations, tests, or seasonality.

Tests

@@

Two particularly important areas:
\begin{itemize}
    \item Schooling: large costs to pupils, ... social inequalities
    \item Work: Q2 / 2020 saw the largest drop in GDP in a long time;
\end{itemize}

>>>>

\begin{figure}
\centering
        \includegraphics[width=\textwidth]{../figures/results/figures/full_decomposition_rapid_tests_area}
        \caption{Decomposition of Rapid Tests}
\end{figure}
\begin{figure}
\centering
        \includegraphics[width=\textwidth]{../figures/results/figures/full_decomposition_rapid_tests_bar}
        \caption{Decomposition of Rapid Tests}
\end{figure}

@@

Modelling a population of agents according to actual demographic characteristics means
that we can use a wide array of data to identify and estimate the model's many
parameters.\footnote{See section S.XXX of the supplementary materials for an overview.}
Mobility data is used to model the reductions in work contacts. School and daycare
policies are incorporated directly from official directives. Infection rates by age and
geographical region are estimated to match to officially recorded numbers; so is the
prevalence of virus strains. The model yields total infections, but only a fraction of
those will be officially recorded. We model the fraction of known cases as depicted in
Figure~\ref{fig:model_for_official_cases}.\comment[id=HM]{Add a sentence.}
% \footnote{EQUATIONS FOR THE FOURTH PICTURE (find names!):

%     The probabilities for Figure~\subref{fig:model_for_official_cases} are the
%     following:

%     \begin{align*} x & = \frac{n\_newly\_infected \times share\_known\_cases \times
%         P(PCR | S)}{n\_symptomatic\_and\_untested}                    \\
%         y & = \frac{n\_newly\_infected \times share\_known\_cases \times P(PCR |
%         S)}{n\_asymptoptomatic\_and\_infected\_and\_untested} \\
%         z & = \frac{P(PCR | RT)}{survey} \end{align*} where untested means that
%     individuals are not waiting on the result of a previously administered rapid
%     test.} 
A further advantage is that the simulated data have a structure that resembles datasets
used for regression models, which allows additional plausibility checks by re-running
the same models on the model-generated data.\comment[id=HM]{Only keep if we actually do
something like that.}

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/full_decomposition_channels_area}
        \includegraphics[width=\textwidth]{../figures/results/figures/full_decomposition_channels_bar}

@@

The largest effect---almost one half when considering the decompositions---comes from
rapid testing. Here, it is crucial to differentiate between recorded cases and actual
cases. Additional testing means that infections become known which would otherwise
remain undetected. Figure~\ref{fig:2021_scenarios_recorded} shows that this means that
until late April, recorded cases are higher than in the scenario where none of the three
mechanisms is turned on. Compared to the scenario with vaccinations only, this point is
reached only around mid May and it would be June for the comparison with the
seasonality-only scenario. The effect on total cases, however, is visible immediately.
Despite the fact that only a small fraction of the population performed weekly rapid
tests in March\footnote{X\%\comment[id=HM]{Put in}in the model; 27\% of respondents to
the COSMO study reported in early March that they \textit{ever} did a rapid test)}, new
infections on April 1 would be rise in new infections would be reduced by 53\% relative
to the scenario without vaccinations, rapid tests, or seasonality.

@@

Two of the most contentious NPIs concern schools and mandates to work from home. In many
countries, schools switched to remote instruction during the first wave, so did Germany. They were kept fully open until 
 Two
particularly important areas:
\begin{itemize}
    \item Schooling: large costs to pupils, ... social inequalities
    \item Work: Q2 / 2020 saw the largest drop in GDP in a long time;
\end{itemize}
